\section{The structure of thesis}
\label{sec:structure}

This dissertation consists of 5 Chapters followed the discussion of Bandits Problem. This first Chapter, proposed the background of Bandit problems.

Chapter 2, is about some important strategies of Bandit problem, how to trade off the balance between Exploration/Exploitation. In this chapter, we introduce some methods very useful and effective to keep balance for the tradeoff. Furthermore, to analyze their advantage and disadvantage with principal theorem and empirical experiments. The classical Bandit problem, Multi-Armed Bandit problem, will be introduced. Recently, there are many researches working in this setting. We concentrate on its environment, lower bound, gittins index and best arm identification etc.

Chapter 3, it's the classification problem under Bandit Feedback. Here, we proposed several algorithms in the-state-of-art to solve the problems in multiclass or multilabel classification. Compared those algorithms, we will introduce the algorithms who related or modified from those classification algorithms. At last, compare their effectiveness or regret bound by empirical experiments based on those common data sets.

Chapter 4, it is the extension of Multi-Armed Bandit that each arm has multi-objective. So many domains are met this problem, i.e. supply chain, some decision system, Big data platform and so on. In this chapter, we will introduce some traditional way to solve this problem, and our contribution, a novel method who works more effectively and more precisely.

Chapter 5, also the last chapter. We will make the conclusion of all chapters in this part.